


\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{amsthm}
\usepackage{amsthm,amsmath,amsfonts,amssymb,amstext}
\usepackage{latexsym,ifthen,url,rotating}
\usepackage[usenames,dvipsnames]{color}


% --- -----------------------------------------------------------------
% --- Document-specific definitions.
% --- -----------------------------------------------------------------
\newtheorem{definition}{Definition}

\newcommand{\concat}{{\,\|\,}}
\newcommand{\bits}{\{0,1\}}
\newcommand{\Range}{{\mathrm{Range}}}
\newcommand{\A}{{\mathcal{A}}}

% --- -----------------------------------------------------------------
% --- The document starts here.
% --- -----------------------------------------------------------------
\begin{document}
%\maketitle

\noindent CS513: Design and Analysis of Data Structures and Algorithms \\
        Group: Stewart Smith and Kaushal Parikh\\

        \begin{center}
        \LARGE{\textbf{Homework 3}}\\
            \end{center}

            \vspace{.1in}


            \begin{enumerate}

            \item \\
            Maintain a heap of size $k+1$.  To insert the first k+1 elements into the heap is O(k).
            I would then retrieve the smallest element from the heap in O(logk) time and put it into
            a sorted array.  Then we could take the k+2 element from the unsorted array and insert it
            into the heap.  This final run time would be O(nlogk).
            \item \\
            \item \\
            We need to prove that a \& b $\implies$ c, a \& c $\implies$ b, and b \& c $\implies$ a\\
            \newline
            Statement b) is equivalent to $edges\geq n-1$\\
            We prove this through induction.  Base case $n=2$, $edges\geq1$\\
            Assume: with n nodes $edges\geq n-1$\\
            Prove: with $n+1$ nodes $edges\geq n$\\
            Suppose that graph G has n nodes and $n-1$ edges.  Graph G' is identical to G but with
            one more vertex than G.  In order to make G identical to G' we need to add one vertex and
            to connect it, 1 edge.
            \newline
            \newline
            Statement c) is equivalent to $edges\leq n-1$\\
            This is also proven through induction
            Base case $n=2$, $edges\leq1$\\
            Assume: with n nodes $edges\leq n-1$\\
            Prove: with $n+1$ nodes $edges\leq n$\\
            Suppose that graph G has n nodes and $n-1$ edges.  Graph G' is identical but with n edges
            We can only make G and G' identical by deleting an edge from G'.  G' has a cycle because all
            n edges connect n nodes with 1 edge left over.  This edge makes a cycle.
            \item \\ a) \\
            \item \\
            $F(n+2) = F(n+1) + F(n)$\\
            $F(n+1) = F(n) + F(n-1)$\\
            \vdots\\
            $F(2) = F(1) + F(0)$\\
            $F(1) = F(0) + 1$\\
            \item \\
            Take each element in the unsorted array and make it a node in graph G.  Node $u$ is the smallest
            element and node $v$ is the largest element.  If we construct edges between all nodes of the graph
            and we run Ham-Path on the graph, one of the paths will be the sorted array.  With a polynomial run-time
            for Ham-Path, we have found a polynomial run-time for sorting.
            \item \\ Reduce Hamiltonian path to BDST\\
                1) Given a graph G with vertices U and V. Create a Graph M by attaching new nodes P & Q respectively to U and V.\\
                2) Let k represent the max number of edges and let k = 2. BDST(M,K=2) forces the spanning tree to be a path. Connect P $&$ Q to force the path to start and end with U and V. We reduced the hamiltonian path to BDST. The hamiltonian path, therefore isn't polynomial, and implies that BDST isn't polynomial either.
            \end{enumerate}

                                \end{document}

